\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\begin{document}
	In this document we examine the potentiometer in a number of circuits, 
	including in series, parallel, and singleton circuits (i.e. one with just 
	the potentiometer and a power supply).
	\section{Definition}
	A potentiometer is a passive device with three terminals and a variable 
	resistance of '$R_P$' ohms.  Said resistance is a function of the angle, 
	denoted as '$\theta$', of the knob attached to the device.
	\section{Presuppositions}
	In all of the circuit applications contained in this document there is 
	supposed to be a power supply with a voltage of $E$ volts.  Said voltage 
	may be variable and a function of time or constant.
	\section{Singleton}
	The circuit equation is:
	\begin{equation}\label{eq:V_P}
		E = V_P = R_P \cdot i
	\end{equation}
	Since the supplied voltage does not change in response to the angle of the 
	knob -- i.e. $E$ is not a function of $\theta$ -- only the current, denoted 
	as '$i$', can change as a function of $\theta$.
	$$ i(\theta) = \frac{E}{R_P(\theta)}$$
	If $E$ changes with time, we need to introduce time, denoted as '$t$', to 
	the equation and subsequently, the function that gives the current, making 
	it a multivariate function.
	$$ i(t, \theta) = \frac{E(t)}{R_P(\theta)}$$
	\section[Series]{In Series}
	As is the case with a singleton circuit, only the current changes with the 
	angle of the knob;  The supplied voltage is not a function of $\theta$.
	\subsection[Resistor]{With Another Resistor}
	Suppose there is a circuit with a pentiometer and a resistor with 
	a resistance of $R$ ohms.  The voltage running across this resistor is 
	proportional to the current running through the circuit.  This means that 
	changes in $\theta$ lead to changes in the voltage running across said 
	resistor and the potentiometer.  In other words, turning the knob 	
	\emph{divides} the voltage between the two components.
	\subsection[Capacitor]{With a Capacitor}
	Now suppose there is a circuit with a potentiometer and a capacitor with a 
	capacitance of $C$ farads.
	$$ E = V_P + V_C$$
	Here, '$V_C$' denotes the voltage running across the capacitor which is 
	given by:
	\begin{equation}\label{eq:V_C}
		V_C = \frac{1}{C} \int i \cdot dt
	\end{equation}
	Via the first equation of this subsection, the above equation, equation 
	(\ref{eq:V_P}), and substitution we end up with the following 
	integral-differential equation:
	$$ E = R_P \cdot i + \frac{1}{C} \int i \cdot dt$$
	To turn this into a differential equation that can be used to solve for the 
	current in terms of time we first must consider the function that gives $i$ 
	a uni variate function with $t$ as the variable and $\theta$ as the 
	parameter.  This is because the charge in the capacitor, which is a factor 
	of $V_C$, is equal to the primitive integral of the current with respect to 
	time;  Thus, to turn the above equation into a differential equation we 
	must \emph{fully} differentiate throughout as opposed to \emph{partially} 
	differentiate throughout with respect to time.  And doing so gives, 
	assuming the supplied voltage is constant, gives:
	$$ R_P \cdot i' + \frac{1}{C} i = 0$$
	The general solution is of the form:
	$$ i := i(t) := i(t \vert \theta) = Ae^{mt}$$
	where $A \in \mathbb{R}$ is an arbitrary constant to be solved for using 
	some initial value problem (IVP) and $m$ is the root of the auxiliary 
	equation:
	$$ R_P \cdot m + \frac{1}{C} = 0$$
	$$ CR_P \cdot m + 1 = 0$$
	$$ m := m(\theta) = - \frac{1}{CR_P(\theta)}$$
	Remember that $\theta$ is a parameter of the function that gives the 
	current.  In other words, $\theta$ is considered a constant when 
	differentiating or integrating with respect to the independent variable, 
	time or $t$. \\ \\
	For the IVP let $q$ be defined as:
	$$ q:=q(t) := \int i \cdot dt$$
	And, the IVP is:
	$$ E = R_P \cdot i(0) + \frac{1}{C} q(0)$$
	$$ E - \frac{1}{C}q(0) = R_P \cdot i(0) $$
	$$ i(0) = i(0 \vert \theta) = A(\theta) = \frac{E}{R_P(\theta)} + 
	m(\theta)q(0)$$
	\section[Parallel]{In Parallel}
	Recall that a potentiometer has three terminals.  These terminals usually 
	form a linear array.  Whatever shape they form, let the paradigm be 
	such that the first and last terminals are the poles of the voltage drop 
	when the potentiometer is in a series circuit.  The first and last 
	terminals are denoted as '$T$' and '$B$' respectively, while the middle 
	terminal is denoted as '$M$'. \\ \\
	With this paradigm, the magnitude of the voltage running across the 
	potentiometer is equal to the magnitude of the voltage drop from terminal 
	$T$ to terminal $B$.
	\begin{equation}\tag{\ref{eq:V_P}}
		|V_P| = |V_{TB}| = |R_P \cdot i|
	\end{equation}
	The above principle makes no assumption about the polarity of said voltage 
	drop.  Assuming $T$ has a polarity of $(+)$ and that this also the 
	polarity in the previous sections, the voltage drop from $T$ to $B$ is 
	equal to the voltage running across the potentiometer.
	\begin{equation}\tag{\ref{eq:V_P}}
		V_P = V_{TB} = R_P \cdot i
	\end{equation}
	\subsection[Resistor]{With Another Resistor}
	Suppose there is a parallel circuit with a potentiometer that is partially 
	in parallel and partially in series with a resistor with a resistance of 
	$R$ ohms.  We say 'partially' because $T$ to $M$ is in series with $M$ to 
	$B$ and with said resistor, while $M$ to $B$ is in parallel with the 
	resistor.
	$$ E = V_{TM} + V_R = V_{TM} + V_{MB} = V_P$$
	Breaking it down by each voltage drop, we have the following:
	$$ V_{TM} = R_{TM}(i_1 + i_2)$$
	$$ V_{MB} = R_{MB}\cdot i_1$$
	$$ V_R = R \cdot i_2$$
	Since there are two current to solve for, we need two unique equations.  
	Thankfully, via the first equation of this subsection, we have them.
	$$ V_{TM} + V_R = V_{TM} + V_{MB}$$
	$$ V_R = V_{MB}$$
	$$ R \cdot i_2 = R_{MB} \cdot i_1$$
	As for the second equation:
	$$ V_{TM} + V_{MB} = E$$
	$$ R_{TM}(i_1 + i_2) + R_{MB}\cdot i_1 = E$$
	If both currents are already given and we simply want to find the 
	resistance of the potentiometer ($R_P$) then we can use the following 
	equation:
	$$ E = \frac{i_1 + i_2}{\frac{1}{R_P} + \frac{1}{R}}$$
	$$ E \left(\frac{1}{R_P} + \frac{1}{R} \right) = i_1 + i_2$$
	$$\frac{E}{R_P} = i_1 + i_2 - \frac{E}{R} $$
	$$ R_P = \frac{E}{i_1 + i_2 - \frac{E}{R}}$$
\end{document}
